---
title: "Shiny exercises"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
# include something so it installs the package if not there 9or shiny apps.io
library(learnr)
library(readr)
knitr::opts_chunk$set(echo = FALSE)

# Loading data
# rii_sii_ethnicity <- read_csv("data/RII_SII_by_ethnicity_age_dep_2011.csv")
# st_rates_ethnicity <- read_csv("data/st_rates_by_ethnicity_age_dep_2011.csv")


```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r shiny-test, exercise=TRUE}
###############################################.
## UI ----
###############################################.
ui <- fluidPage("Scotland Test", 
                h3("Hello World!"),
                br()
                # selectInput("age", "Select age group", choices = age_grps),
                # selectInput("depr", "Select deprivation group", choices = depr_grps),
                # plotOutput("barplot")
                
) # fluidPage bracket

###############################################.
## Server ----
###############################################.

server <- function(input, output, session) {
#   
#   # Filtering data based on user input
# st_rates_filtered <- reactive({
#   st_rates_ethnicity %>% 
#     filter(age == input$age &
#              ses == input$depr)
# })
# 
#   output$barplot <- renderPlot({
#     ggplot(st_rates_filtered(), aes(x = ethnicity, y = rate)) +
#       geom_bar(stat = "identity")
#   })
  
} # end of server

shinyApp(ui = ui, server = server) # Running the app

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

